---
title: "Data profile `r params$exam ` "
author: "Inserm1138"
date: "`r format(Sys.time(), '%d %B %Y') `"
output: html_document
params:
    exam: exam
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('./init.R')
name_exam <- params$exam
# name_exam <- "BIO:20180213114053"
# name_exam <- listecalc[1]
# name_exam <- "BIO:1388"
# name_exam <- "BIO:1145"
# name_exam <- "BIO:1024"
# name_exam <- "BIO:1052"
# name_exam <- "BIO:1000"
# name_exam <- "BIO:1195"
# name_exam <- "BIO:1007" (Trou anionique)
# name_exam <- "BIO:1007"
#name_exam <- "BIO:1975"
```


```{r setupglobal, include=FALSE, cache=FALSE}
Listcount <- read.csv2(paste0(rept,"Count.csv"), stringsAsFactors = FALSE)
source(paste0(rept2,'loadresults.R'))
```

```{r loaddata}
title_exam <- paste0(name_exam," / ",Listcount$NAME_CHAR[which(Listcount$CONCEPT_CD==name_exam)] )
basebio1 <- loaddata(name_exam)
basebio1 <- basebio1[which(!is.na(basebio1$value)),]
idx <- findInterval(basebio1$value,quantile(basebio1$value, probs = c(0.01,0.99)),rightmost.closed = T) %in% 1
result_exam <- result[which(result$CONCEPT_CD==name_exam),]
# Generate graph of data
exam_breakpoints <- result_breakpoints[which(result_breakpoints$exam==name_exam),]
exam_discretization <- discretization_times[which(discretization_times$exam==name_exam),]
dates_bp <- tryCatch(as.numeric(unlist(strsplit(exam_breakpoints$Dates,split = "@"))), error = function(e) NA)
dates_discret <- ifelse(nrow(exam_discretization)==0,NA,exam_discretization$startT)
exam_missingdata <- missingdata_list[which(gsub(".",":", fixed=T, missingdata_list$namefile)==name_exam),]
result_exam$missingdata <- ifelse(length(exam_missingdata$startT_MD)>0,T,F)
```

# Presentation of data : `r title_exam `

* There are `r length(basebio1$value)` values between  `r as.Date(min(basebio1$date))` and `r as.Date(max(basebio1$date))`. 
* Median and IQR are `r sprintf("%s [%s - %s]",quantile(basebio1$value, probs = 0.5),quantile(basebio1$value, probs = 0.25),quantile(basebio1$value, probs = 0.75))`.
* The minimum value is `r min(basebio1$value)`.
* The maximum value is `r max(basebio1$value)`.

## Data density

```{r graphdensity}
ggplot(basebio1[idx,], aes(value, fill ="red")) +
  geom_density() + theme_bw() + ggtitle(title_exam) + guides(fill=FALSE)
```

# Analyse of time serie

## Detections

Results of detection methods:

+ Breakpoint: `r ifelse(result_exam$breakpoint==TRUE,"Yes","Undetectable")`
+ Trends: `r ifelse(result_exam$trends==TRUE & result_exam$PropVar>0,"Yes","Undetectable")`
+ Change of distribution: `r ifelse(result_exam$discretization==TRUE,"Yes","Undetectable")`
+ Missing data: `r ifelse(result_exam$missingdata==TRUE,"Yes","Undetectable")`

## Data over time

Breakpoint (blue dashed line); Change of distribution (red dashed line); Missing data (pink dashed line)


```{r graphtime}
creatfig(x=name_exam,y=name_exam)
```

## Detections analysis

Results of detected changes:

+ Breakpoint: `r ifelse(result_exam$breakpoint==TRUE,paste0(as.Date(dates_bp),collapse = " / "),"--")`
+ Change of distribution: `r ifelse(result_exam$discretization==TRUE, paste0(as.Date(exam_discretization$startT),collapse = " / ") ,"--")`
+ Missing data: `r ifelse(result_exam$missingdata==TRUE, paste0(as.Date(unique(exam_missingdata$startT_MD)),collapse="/"),"--" )`
+ Trends: `r ifelse(result_exam$trends==FALSE | result_exam$PropVar==0,"--", ifelse(result_exam$trends==TRUE & result_exam$PropVar>5, "High", ifelse(result_exam$trends==TRUE & result_exam$PropVar<=5,"Low","--" )) )`

### Number of observations

```{r graphtime2}
ggplot(basebio1[idx,], aes(x=as.Date(date), fill ="red")) +
  geom_histogram(binwidth = 60) + theme_bw() + ggtitle(title_exam) + guides(fill=FALSE) +  xlab("Time")+ ylab("Number of exams")
```

### Global detections

```{r graphtimeglobal}
#
numevents2 <- numevents
if(!is.na(dates_bp)){
  numevents2 <- numevents2 + geom_vline(data=data.frame(bp=dates_bp),aes(xintercept = bp),linetype = "dashed", colour = "blue")
}
if(!is.na(dates_discret)){
  numevents2 <- numevents2 + geom_vline(data=data.frame(discret=dates_discret),aes(xintercept = discret),linetype = "dashed", colour = "#fb739c")
}
if(nrow(exam_missingdata)>0){
  numevents2 <- numevents2 + geom_vline(data=data.frame(discret=unique(exam_missingdata$startT_MD)),aes(xintercept = discret),linetype = "dashed", colour = "#ff33ec")
}
numevents2
```
