---
title: "Biology quality and CDW"
author: "INSERM1138eq22"
date: "31 août 2017"
output:
  html_document: default
  pdf_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE)
```

```{r cars, echo=F, results='hide'}
library("DT")
```

The objective of these scripts is to provide diagnostic tools of the quality of biological data in a clinical data warehouse.
These scripts are based on: (REF ARTICLE).

# Data input

Examples files have to be put in a directory called 'Example' in the working directory.

## Example of the list of exam
```{r listeexample, echo=F,warning=FALSE, message=FALSE}
source('./init.R')
list_example <- read.csv2(paste0(rept2,"./Example/Count.csv"), stringsAsFactors = FALSE)
datatable(list_example[,1:4], class = 'cell-border stripe')
```

## Example of a dataset of one exam
```{r dataexample, echo=F,warning=FALSE}
data_example <- read.csv2(paste0(rept2,"./Example/BIO.20170821101046.csv"), stringsAsFactors = FALSE)
datatable(data_example, class = 'cell-border stripe')
```

# Scripts

## Structure

There are 13 R files :

+ init.R: load packages, create directories
+ datasimu.R: simulation of data to test the programs
+ datareal.R: extract files from i2b2 clinical data warehouse
+ movingquantiles.R
+ fun_movingquantiles.R
+ missingdata.R
+ fun_missingdata.R
+ discretization.R
+ fun_discretization.R
+ breakpoints.R
+ fun_breakpoints.R
+ trends.R
+ fun_trends.R

Plus one directory called 'Example'. It contains files in the right format.
  
## How to use scripts without real data ?

You need to adapt the script dayareal.R. Ouputs have to be in the same format than files in the directory Example\.  
  
## How to use scripts with real data ?
